Revision of MS #2018:11:32569:0:0:REVIEW

### 2019-02-11 docs/reviews.Rmd
Updated, ready to resubmit

We appreciate the professional way in which our manuscript has been handled. Here we address each issue, suggestion, and comment raised by yourself and both reviewers. We include the original comment in plain text, and present our responses in italics.

@@

- *We chose to keep the word "major" in L26 (now L30) to maintain consistency with the authors' original wording, but we have included quotations to denote this.*

- *In L142 (Now L150) We now say that "ex situ parameters can result in erroneous weight estimates"*

- *Ass suggested, we have changed "major" from L175 to "key" (now L206).*

@@

*"impacts" has been replaced with "negative effects" in L47, now L49*

@@

*We have improved the wording in the original sentence and no longer use the word "know"/"known". The paragraph now starts in L59.*

@@

*The Bahamas are now reported as part of the Western Atlantic Ocean. Text in L82 (now L81-82) and Table 2 (now Table 1) reflect these changes.*

@@

*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L120.*

@@

*We have included the URL in the main text (L129), but the decision to leave it there depends on the editorial formatting. However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the URL to be included.*

@@

*That is correct. We have modified the text to that it reads "each of the different pairs of parameters" (L137)*

@@

*We have reworded the paragraph to make it more clear. Specifically, we report the smallest and largest mean estimated weights for the 109 organisms from the central Mexican Caribbean. We then report their corresponding mean predicted-to-observed ratios, which are still averaged for each pair of parameters across all organisms. These correspond to the first and last "violins" in Fig 4. We then provide the extreme values of predicted-to-observed ratios for all organisms and all studies; In a sense, the worst relative over- and underestimations (the smallest and largest values shown in Fig.4 overall). Finally, we provide similar measures for estimated total biomass (that is, the summ of the 109 predicted weights) by study, relative to the actual true observed total biomas. This last measure is now presented in Fig 5.*

@@

*Yes, we refer to the spatial heterogeneity. We have modified the text so it reads "...lionfish exhibit highly variable, spatially heterogeneous allometric relationships across their invaded range, and...". This is now L161.*

@@

*This was meant to say "We show that", and has now been corrected in what is now L162.*

@@

*Other studies do not report the time of the year when these were collected. However, we recognize this may be a factor that influences weight or growth and therefore the length-weight relationship. We have mentioned that our parameters for the central Mexican Caribbean are from organisms collected during the Summer (L101), and have devoted a paragraph in the discussion (L185) to highlight the importance of collection methods and timing when estimating length-weight relationships.*

@@

*We also expected estimates from spineless weight to underestimate of total weight, however this wasn't the case, and as Reviewer 2 noted, data from Fogg et al. (2013) produced some of the largest estimates. After a careful evaluation of their paper, we noted that their Table 1, in fact, reports TW to TL conversions by gender and for pooled genders. That is, the wording in their paper confused us and made us think they reported spineless weight, but they report total weight. The corresponding modifications have been made in the text. Their paper can be found in this link: https://lionfish.co/wp-content/uploads/2013/05/Distribution-of-Lionfish-in-the-Gulf-of-Mexico.pdf*

@@

*We have expanded on the role of these different sampling and processing methods and devoted a paragraph in the discussion (L185).*

*In terms of the OLS regression versus a mixed modeling approach: in our original manuscript we failed to clearly articulate that our OLS regression was only performed to estimate the length-weight relationship for the 109 organisms from the central Mexican Caribbean (Fig 2). We agree that a GLMM with location modeled as a random effect would properly estimate the "location effect" of the length-weight relationship across the different study sites, both by identifying whether differences exist and by describing the magnitude of these differences. Unfortunately, for this we would need to either have the raw data from all the reviewed studies or perform a region-wide collection that would allow us to have standardized data - both of which were outside the scope of this study. The fact that similar comments were raised by Rev2 suggests that we did not adequately describe this limitation in our original manuscript. We now explicitly state that we did not have access to the raw data from the published studies (L87, L117 and L189). However, it is important to note that the objective of our study was not to describe the biological differences in length-weight relationships between site locations, rather to assess the effect of using ex situ vs. in situ parameter values to estimate lionfish weights from direct length observations (i.e., to assess whether ex situ parameter values result in large errors in weight estimates). We believe that after modifying the text to clearly state our objectives (L87, L117 and L189) and including discussion paragraphs about the limitations of our study (L185 and 196), we have satisfactorily addressed these concerns.*

@@

*We now use the word "key" (L208).*

@@

First, ratio data isn’t distributed normally, and has unqiue behaviors near the tails of the distribution. It should always be transformed, preferably using a logit transformation, prior to analysis.

@@

*The reviewer is correct in that we apply the parameters for lengths that may be outside the ranges originally used to estimate such parameters. We have included a paragraph in the discussion where we compare our range of TLs (34 - 310 mm) to the ranges used by different studies to estimate their parameters (Paragraph starts in L 196). We also make reference to a new supplementary table where we report all information recorded in other studies.*

@@

*In terms of ANCOVA use: this is a similar comment to that raised by Rev1, who suggested the use of a GLMM with locations as random effects that induce variation in the length-weight estimates. As in that case, we agree that an ANCOVA applied to the raw length-weight information would identify if differences exist between locations. However, we do not have the raw data from other studies and applying this to the predicted estimates would not help us answer this question. In a sense, we would be asking if the lines in Fig 3 (with no variance / process error around them) have significantly different slopes and intercepts. As mentioned in the response to R1, we originally failed to clearly state that we do not have the raw data required to perform such an analysis. We have included statements in the methods (L87, L117 and L189) and a discussion paragraph (L185) that highlight these limitations and clarify our objectives/analyses.*

@@

The recommendation for major improvement is in the Discussion, related to the interpretation of their findings. The authors focus mainly on the implications of their findings, in a general way, but offer no potential explanations for the results they observed. Do the patterns of variation in weightlength relationships for invasive lionfish align with the genetic results that have been published? Are they aligned spatially... do populations that are closer geographically have more similar growth relationships? Are there potential effects of depth/season? Did any studies demonstrate a sufficient lack of contrast in total length data to generate a weight-length relationships representative of the entire population in that region? A paragraph or two of Discussion on plausible explanations for the patterns they observed would be a valuable addition.

*As stated above, these were also raised by Rev1. We believe that our modifications to the discussion in L185 and L196 now explicitly mention these issues. And while we cannot test for the influence of all these factors on the length-weight relationship, we can still show that using ex situ parameters that follow different sampling collections and without a standardized collection date may lead to over- and underestimation of total weight.*

*More specifically, paragraph starting in L176 mentions that the spatial patterns in length-weight relationships i) ressemble those observed for length-at-age (Pusack et al 2016), ii) Groups identified by post hoc tests aligned with the spatial distribution of examined studyes and ii) These groups also correspond to genetic analyses (Betancur-R et al 2011).*

*In the new paragraph starting in L185 we now mention that variation can also be caused by other factors that are not related to space. These include different sampling methods, seasonality, and depth ranges.*

@@

*That is correct, the 0.80 and 1.76 values make reference to the mean ratios. We have modified the text to make this clear, but believe that it is important to explicitly state that the maximum under- and overestimations were by a factor of 0.36 and 3.51 - especially because we are unable to assess the full length-weight relationships from all studies given our lack of raw data. We believe the new text justifies including these extremes. The paragraph now starts in L136.*

>>>>

We appreciate the professional way in which our manuscript has been handled. Here we address each issue, suggestion, and comment raised by yourself and both reviewers. We include the original comment in plain text, and present our responses in italics. When relevant, we mention the new line numbers where changes have been made.

@@

- *We chose to keep the word "major" in L26 (now L29) to maintain consistency with the authors' original wording, but we have included quotations to denote this.*

- *In L142 (Now L151) We now say that "the use of ex situ parameters led to significantly erroneous estimates of individual weight and total biomass for lionfish"*

- *Ass suggested, we have changed "major" from L175 to "key" (now L211).*

@@

*"impacts" has been replaced with "negative effects" in L47, now L48*

@@

*We have improved the wording in the original sentence and no longer use the word "know"/"known". The paragraph now starts in L58.*

@@

*The Bahamas are now reported as part of the Western Atlantic Ocean. Sentence starting in L82 and Table 2 (now Table 1) reflect these changes.*

@@

*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L120-121.*

@@

*We have included the URL in the main text (L130), but the decision to leave it there depends on the editorial formatting. However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the URL to be included.*

@@

*That is correct. We have modified the text to that it reads "each of the different pairs of parameters" (L138)*

@@

*We have reworded the paragraph to make it more clear. Specifically, we report the smallest and largest mean estimated weights for the 109 organisms from the central Mexican Caribbean. We then report their corresponding mean predicted-to-observed ratios, which are still averaged for each pair of parameters across all organisms. These correspond to the first and last "violins" in Fig 4. We then provide the extreme values of predicted-to-observed ratios for all organisms and all studies; In a sense, the worst relative over- and underestimations (the smallest and largest values shown in Fig.4 overall). Finally, we provide similar measures for estimated total biomass (that is, the sum of the 109 predicted weights) by study, relative to the actual true observed total biomass. This last measure is now presented in Fig 5.*

@@

*Yes, we refer to the spatial heterogeneity. We have modified the text so it reads "...lionfish exhibit highly variable, spatially heterogeneous allometric relationships across their invaded range, and...". This is now L164.*

@@

*This was meant to say "We show that", and has now been corrected in what is now L165-166.*

@@

*Other studies do not report the time of the year when these were collected. However, we recognize this may be a factor that influences weight or growth and therefore the length-weight relationship. We have mentioned that our parameters for the central Mexican Caribbean are from organisms collected during the Summer (L101), and have devoted a paragraph in the discussion (L188) to highlight the importance of collection methods and timing when estimating length-weight relationships.*

@@

*We also expected estimates from spineless weight to underestimate of total weight, however this wasn't the case, and as Reviewer 2 noted, data from Fogg et al. (2013) produced some of the largest estimates. After a careful evaluation of their paper, we noted that their Table 1, in fact, reports TW to TL conversions by gender and for pooled genders. That is, the wording in their paper confused us and made us think they reported spineless weight, but they report total weight. The corresponding modifications have been made in the text by deleting that sentence. Their paper can be found in this link: https://lionfish.co/wp-content/uploads/2013/05/Distribution-of-Lionfish-in-the-Gulf-of-Mexico.pdf*

@@

*We have expanded on the role of these different sampling and processing methods and devoted a paragraph in the discussion (L188).*

*In terms of the OLS regression versus a mixed modeling approach: in our original manuscript we failed to clearly articulate that our OLS regression was only performed to estimate the length-weight relationship for the 109 organisms from the central Mexican Caribbean (Fig 2). We agree that a GLMM with location modeled as a random effect would properly estimate the "location effect" of the length-weight relationship across the different study sites, both by identifying whether differences exist and by describing the magnitude of these differences. Unfortunately, for this we would need to either have the raw data from all the reviewed studies or perform a region-wide collection that would allow us to have standardized data - both of which were outside the scope of this study. The fact that similar comments were raised by Rev2 suggests that we did not adequately describe this limitation in our original manuscript. We now explicitly state that we did not have access to the raw data from the published studies (L87, L117-118 and L195-198). However, it is important to note that the objective of our study was not to describe the biological differences in length-weight relationships between site locations, rather to assess the effect of using ex situ vs. in situ parameter values to estimate lionfish weights from direct length observations (i.e., to assess whether ex situ parameter values result in large errors in weight estimates). We believe that after modifying the text to clearly state our objectives (L71 and L116-119) and including discussion paragraphs about the limitations of our study (L188 and 201), we have satisfactorily addressed these concerns.*

@@

*We now use the word "key" (L211).*

@@

First, ratio data isn’t distributed normally, and has unique behaviors near the tails of the distribution. It should always be transformed, preferably using a logit transformation, prior to analysis.

@@

*The reviewer is correct in that we apply the parameters for lengths that may be outside the ranges originally used to estimate such parameters. We have included a paragraph in the discussion where we compare our range of TLs (34 - 310 mm) to the ranges used by different studies to estimate their parameters (Paragraph starts in L 201). We also make reference to a new supplementary table where we report all information recorded in other studies.*

@@

*In terms of ANCOVA use: this is a similar comment to that raised by Rev1, who suggested the use of a GLMM with locations as random effects that induce variation in the length-weight estimates. As in that case, we agree that an ANCOVA applied to the raw length-weight information would identify if differences exist between locations. However, we do not have the raw data from other studies and applying this to the predicted estimates would not help us answer this question. In a sense, we would be asking if the lines in Fig 3 (with no variance / process error around them) have significantly different slopes and intercepts. As mentioned in the response to R1, we originally failed to clearly state that we do not have the raw data required to perform such an analysis. We have included statements in the methods (L87, L117-118) and a discussion paragraph (L195-198) that highlight these limitations and clarify our objectives/analyses.*

@@

The recommendation for major improvement is in the Discussion, related to the interpretation of their findings. The authors focus mainly on the implications of their findings, in a general way, but offer no potential explanations for the results they observed. Do the patterns of variation in weight-length relationships for invasive lionfish align with the genetic results that have been published? Are they aligned spatially... do populations that are closer geographically have more similar growth relationships? Are there potential effects of depth/season? Did any studies demonstrate a sufficient lack of contrast in total length data to generate a weight-length relationships representative of the entire population in that region? A paragraph or two of Discussion on plausible explanations for the patterns they observed would be a valuable addition.

*As stated above, these were also raised by Rev1. We believe that our modifications to the discussion in L188 and L201 now explicitly mention these issues. And while we cannot test for the influence of all these factors on the length-weight relationship, we can still show that using ex situ parameters that follow different sampling collections and without a standardized collection date may lead to over- and underestimation of total weight.*

*More specifically, paragraph starting in L179 mentions that the spatial patterns in length-weight relationships i) resemble those observed for length-at-age (Pusack et al 2016), ii) Groups identified by post hoc tests aligned with the spatial distribution of examined studies and ii) These groups also correspond to genetic analyses (Betancur-R et al 2011).*

*In the new paragraph starting in L188 we now mention that variation can also be caused by other factors that are not related to space. These include different sampling methods, seasonality, and depth ranges.*

@@

*That is correct, the 0.80 and 1.76 values make reference to the mean ratios. We have modified the text to make this clear, but believe that it is important to explicitly state that the maximum under- and overestimations were by a factor of 0.36 and 3.51 - especially because we are unable to assess the full length-weight relationships from all studies given our lack of raw data. We believe the new text justifies including these extremes. The paragraph now starts in L137.*
